---
title: "File S4: Contamination Analysis"
author: "Eric S. Tvedte"
date: "February 17, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Usage

Assessment of contamination was assessed by mapping reads from Riptide to a reference sequence containing all genomes used in the experiment. 

##Filter 1: Species assignment, retain primary reads  
###Load / format data
```{r setup1}
in.path = "Y:/RDRIP/etvedte/Contamination/Filter1/final_species_map_compiled.txt"
file <- read.table(in.path, header = F, sep = '\t')

file[is.na(file)] <- 0

#reorder file based on well number
x <- file[order(file[12,])]
#remove well number from file
x <- x[-c(12), ]

#write out reordered file as sanity check
write.table(x, file = "Y:/RDRIP/etvedte/Contamination/Filter1/reordered_species_map_compiled.txt", sep = '\t', col.names = FALSE, row.names = FALSE, quote = FALSE)

new.file <- read.table("Y:/RDRIP/etvedte/Contamination/Filter1/reordered_species_map_compiled.txt", header = T, sep = '\t')

new.file[is.na(new.file)] <- 0
```

###Generate legend for Riptide samples
```{r legend1, fig.height=6, fig.width=6, fig.align="center"}
#optional pdf output
#pdf("Y:/RDRIP/etvedte/Contamination/Filter1/RIPTIDE_Filter1_speciesmap_legend.pdf")

  #make legend
  rip.col <- c('#e6194b', '#3cb44b', '#ffe119', '#4363d8', '#f58231', '#911eb4', '#46f0f0','#f032e6', '#bcf60c', '#fabebe')
  plot(NULL ,xaxt='n',yaxt='n',bty='n',ylab='',xlab='', xlim=0:1, ylim=0:1)
  legend(x = "center", y = NULL, legend = paste(new.file[,1]), text.col = rip.col)
#optional pdf close
#dev.off()
```

###Generate pie charts for Riptide plate wells
```{r mapfilt1, fig.height=6, fig.width=6, fig.align="center"}

#optional pdf output
#pdf("Y:/RDRIP/etvedte/Contamination/Filter1/RIPTIDE_Filter1_speciesmap_wells_new.pdf", height = 6, width = 6)

  #set up grid for visualization
  par(mfrow = c(12,12))
  par(mar = c(0.25,0.25,0.25,0.25))

  #set maxmap variables
  count90 = 0
  count95 = 0
  count99 = 0

  #iterate over each well
  for (i in 2:97){
    new.file[,1] <- as.character(new.file[,1])
  
    new.file[,i] <- (new.file[,i] / sum(new.file[,i]) * 100)

    new.file[,i] <- round(new.file[,i], 2)

    slices <- new.file[,i]
    #lbls <- new.file[,1]
    pct <- round(slices/sum(slices)*100)
    pie(new.file[,i], labels = NA, col=rip.col, radius = 1)
    #title(main = toString(colnames(new.file[i])), cex.main = 0.5)
  
    #count wells with maxmap criteria
    if (max(new.file[,i] > 90)){
      count90 = count90 + 1
    }
    if (max(new.file[,i] > 95)){
      count95 = count95 + 1
    }
    if (max(new.file[,i] > 99)){
      count99 = count99 + 1
    }              
  }
#optional pdf close 
#dev.off()

#par(new = TRUE)  
#legend(x = "bottom", y = NULL, legend = paste(file[,1]), text.col = rip.col)
  
print(paste("Number of samples with 90% reads mapping a single species =", count90, sep = " "))
print(paste("Number of samples with 95% reads mapping a single species =", count95, sep = " "))
print(paste("Number of samples with 99% reads mapping a single species =", count99, sep = " "))
```

##Filter 2: Species assignment, retain primary, non- multimapped reads  

```{r setup2, echo = FALSE}
in.path = "Y:/RDRIP/etvedte/Contamination/Filter2/final_species_map_compiled.txt"
file <- read.table(in.path, header = F, sep = '\t')

file[is.na(file)] <- 0

#reorder file based on well number
x <- file[order(file[12,])]
#remove well number from file
x <- x[-c(12), ]

#write out reordered file as sanity check
write.table(x, file = "Y:/RDRIP/etvedte/Contamination/Filter2/reordered_species_map_compiled.txt", sep = '\t', col.names = FALSE, row.names = FALSE, quote = FALSE)

new.file <- read.table("Y:/RDRIP/etvedte/Contamination/Filter2/reordered_species_map_compiled.txt", header = T, sep = '\t')

new.file[is.na(new.file)] <- 0
```


```{r legend2, fig.height=6, fig.width=6, fig.align="center", echo=FALSE}
#optional pdf output
#pdf("Y:/RDRIP/etvedte/Contamination/Filter2/RIPTIDE_Filter2_speciesmap_legend.pdf")

  #make legend
  rip.col <- c('#e6194b', '#3cb44b', '#ffe119', '#4363d8', '#f58231', '#911eb4', '#46f0f0','#f032e6', '#bcf60c', '#fabebe')
  plot(NULL ,xaxt='n',yaxt='n',bty='n',ylab='',xlab='', xlim=0:1, ylim=0:1)
  legend(x = "center", y = NULL, legend = paste(new.file[,1]), text.col = rip.col)
#optional pdf close
#dev.off()
```


```{r mapfilt2, fig.height=6, fig.width=6, fig.align="center", echo=FALSE}

#optional pdf output
#pdf("Y:/RDRIP/etvedte/Contamination/Filter2/RIPTIDE_Filter2_speciesmap_wells_new.pdf", height = 6, width = 6)

  #set up grid for visualization
  par(mfrow = c(12,12))
  par(mar = c(0.25,0.25,0.25,0.25))

  #set maxmap variables
  count90 = 0
  count95 = 0
  count99 = 0

  #iterate over each well
  for (i in 2:97){
    new.file[,1] <- as.character(new.file[,1])
  
    new.file[,i] <- (new.file[,i] / sum(new.file[,i]) * 100)

    new.file[,i] <- round(new.file[,i], 2)

    slices <- new.file[,i]
    lbls <- new.file[,1]
    pct <- round(slices/sum(slices)*100)
    pie(new.file[,i], labels = NA, col=rip.col, radius = 1)
    #title(main = toString(colnames(new.file[i])), cex.main = 0.5)
  
    #count wells with maxmap criteria
    if (max(new.file[,i] > 90)){
      count90 = count90 + 1
    }
    if (max(new.file[,i] > 95)){
      count95 = count95 + 1
    }
    if (max(new.file[,i] > 99)){
      count99 = count99 + 1
    }              
  }
#optional pdf close 
#dev.off()

#par(new = TRUE)  
#legend(x = "bottom", y = NULL, legend = paste(file[,1]), text.col = rip.col)
  
print(paste("Number of samples with 90% reads mapping a single species =", count90, sep = " "))
print(paste("Number of samples with 95% reads mapping a single species =", count95, sep = " "))
print(paste("Number of samples with 99% reads mapping a single species =", count99, sep = " "))
```

##Species assignment, retain primary reads with MAPQ > 30  

```{r setup3, echo = FALSE}
in.path = "Y:/RDRIP/etvedte/Contamination/Filter3/final_species_map_compiled.txt"
file <- read.table(in.path, header = F, sep = '\t')

file[is.na(file)] <- 0

#reorder file based on well number
x <- file[order(file[12,])]
#remove well number from file
x <- x[-c(12), ]

#write out reordered file as sanity check
write.table(x, file = "Y:/RDRIP/etvedte/Contamination/Filter3/reordered_species_map_compiled.txt", sep = '\t', col.names = FALSE, row.names = FALSE, quote = FALSE)

new.file <- read.table("Y:/RDRIP/etvedte/Contamination/Filter3/reordered_species_map_compiled.txt", header = T, sep = '\t')

new.file[is.na(new.file)] <- 0
```


```{r legend3, fig.height=6, fig.width=6, fig.align="center", echo=FALSE}
#optional pdf output
#pdf("Y:/RDRIP/etvedte/Contamination/Filter3/RIPTIDE_Filter3_speciesmap_legend.pdf")

  #make legend
  rip.col <- c('#e6194b', '#3cb44b', '#ffe119', '#4363d8', '#f58231', '#911eb4', '#46f0f0','#f032e6', '#bcf60c', '#fabebe')
  plot(NULL ,xaxt='n',yaxt='n',bty='n',ylab='',xlab='', xlim=0:1, ylim=0:1)
  legend(x = "center", y = NULL, legend = paste(new.file[,1]), text.col = rip.col)
#optional pdf close
#dev.off()
```


```{r mapfilt3, fig.height=6, fig.width=6, fig.align="center", echo=FALSE}

#optional pdf output
#pdf("Y:/RDRIP/etvedte/Contamination/Filter3/RIPTIDE_Filter3_speciesmap_wells_new.pdf", height = 6, width = 6)

  #set up grid for visualization
  par(mfrow = c(12,12))
  par(mar = c(0.25, 0.25, 0.25, 0.25))

  #set maxmap variables
  count90 = 0
  count95 = 0
  count99 = 0

  #iterate over each well
  for (i in 2:97){
    new.file[,1] <- as.character(new.file[,1])
  
    new.file[,i] <- (new.file[,i] / sum(new.file[,i]) * 100)

    new.file[,i] <- round(new.file[,i], 2)

    slices <- new.file[,i]
    lbls <- new.file[,1]
    pct <- round(slices/sum(slices)*100)
    pie(new.file[,i], labels = NA, col=rip.col, radius = 1)
    #title(main = toString(colnames(new.file[i])), cex.main = 0.5)
  
    #count wells with maxmap criteria
    if (max(new.file[,i] > 90)){
      count90 = count90 + 1
    }
    if (max(new.file[,i] > 95)){
      count95 = count95 + 1
    }
    if (max(new.file[,i] > 99)){
      count99 = count99 + 1
    }              
  }
#optional pdf close 
#dev.off()

#par(new = TRUE)  
#legend(x = "bottom", y = NULL, legend = paste(file[,1]), text.col = rip.col)
  
print(paste("Number of samples with 90% reads mapping a single species =", count90, sep = " "))
print(paste("Number of samples with 95% reads mapping a single species =", count95, sep = " "))
print(paste("Number of samples with 99% reads mapping a single species =", count99, sep = " "))
```


```{r session_info, echo = FALSE}
sessionInfo()
#devtools::session_info()
```

Document processed on: `r Sys.Date()` .
